---
title: "CURRICULUM VITAE"
author: Pablo M. Guzm&aacute;n Lizardo

jobtitle: "PhD Candidate in Political Economics at the Stanford Graduate School of Business"
address: "655 Knight Way, Stanford, CA 94305, USA"
fontawesome: yes
email: pablo@guzmanlizardo.com
#github: pguzmanlizardo
#osf: "Enter 5 digit osf string here"
#phone: "+1 438 928 4902"
web: pguzmanlizardo.github.io
#updated: no

keywords: R Markdown, academic CV, template

fontfamily: mathpazo
fontfamilyoptions: sc, osf
fontsize: 11pt
linkcolor: blue
urlcolor: blue

#bibliography: "publications.bib"

format:
  pdf:
    pdf-engine: pdflatex
    template: svm-latex-cv.tex
    geometry: margin=1in
---

# EDUCATION

\vspace{-0.4cm}
\rule{\textwidth}{1pt}

**Stanford Graduate School of Business** *PhD Candidate in Political Economics* \hfill 2021 - Present    
*Fields*: Political Economics, Public Economics, Development Economics.  
**Expected Graduation**: June 2026

**McGill University**, *B.A. Economics and B.A. Political Science* \hfill 2017-2021    
*First Class Honours in Political Science*  
*First Class Honours in Economics*  
*Dean's Honour List*  

# Research and Work Experience

\vspace{-0.4cm}
\rule{\textwidth}{1pt}

**Principal Researcher**, *Impact Evaluation: Motivating Property Tax Compliance*     \hfill 2023-Present      
Co-principal investigator in an impact evaluation of strategies to promote property tax compliance in Kenema, Sierra Leone.  

- a. Increased property tax compliance by over 50 p.p. in the treated groups, doubling tax revenues in the city.
- b. Designed and implemented an impact evaluation of strategies to promote tax compliance. Impacted over 6000 property owners, over a third of city's tax defaulters. 
- c. Collaborated with the local government to design, implement, and evaluate the its tax enforcement policy. 
- d. Coordinated with Chiefly Traditional Authorities to set up a new Traditional Tax Court system to judge over 3000 tax defaulters. 
- e. Collaborated with Muslim and Christian organizations to implement a public campaign motivating tax compliance involving over 3000 tax defaulters.
- f. Led three waves of survey data collection with a team of over 6 research assistants, 4 field coordinators, and over 60 enumerators. 
- g. Over a year of direct, in-field experience in Kenema, Sierra Leone. 
- h. Raised over USD &dollar; 300,000 in research grants to implement this impact evaluation.  

**Principal Researcher**, *Impact Evaluation: Effect of Militarized Policing*      \hfill 2023  
Implemented an impact evaluation of the effects of militarized policing in Dominican Republic. 

- a. Collaborated with the Ministry of Defense, and directly engaged with the Minister and the institution's leadership to initiate and coordinate the evaluation.
- b. Collected and digitize administrative data on patrolling activities in the country. 
- c. Built a novel panel dataset tracking all instances of militarized patrolling in the country between January 2023 and June 2023. 
- d. Applied novel econometric methods to estimate the effect of militarized policing on crime in the country. 

**Graduate Research Assistant**, *Impact Evaluation: Candidate Entry Into Local Government*      \hfill 2022  
Graduate research assistant under Professor Katherine Casey on an experimental intervention that identified, screened, and promoted high-quality potential candidates for political office in Sierra Leone. 

- a. 4 months of in-field, operational assistance in Sierra Leone.
- b. Supervised survey data collection across the country.
- c. Implemented data analysis and manipulation tasks, supporting the project's activities. 

**Undergraduate Research Assistant**, *Impact Evaluation: Micro-savings groups*      \hfill 2018-2021  
Research assistant under Professor Laura Doering on an impact evaluation of micro-savings groups in Colombia. Over 3 years of off-field research, data analysis, and data manipulation support in Stata. 

# Ongoing Research Projects

\vspace{-0.4cm}
\rule{\textwidth}{1pt}

**Does Information about Enforcement Lead to Compliance?**    
*Together with Wilson Prichard and Niccol&ograve; Meriggi*   
Together with the Sierra Leone Association of Journalists, we evaluate the effect of spreading journalistic pamphlets about government tax enforcement action on the likelihood of compliance. We implement a Saturation Experimental Design to evaluate both the direct effect of receiving the pamphlets and the indirect effects of being informed about the pamphlets.   

**Aligning Enforcement Officer Incentives**    
*Together with Wilson Prichard and Niccol&ograve; Meriggi*   
Leveraging a property tax reform in Kenema, Sierra Leone, we evaluate different incentive structures to motive productivity and reduce corruption of tax enforcement officers.   

**Mapping Attitudes Towards Taxation in Sierra Leone**    
*Together with Wilson Prichard and Niccol&ograve; Meriggi*   
Across several city-wide property tax interventions in Sierra Leone, we map the evolution of attitudes towards property taxation and fiscal capacity across time and across several cities.   


# LEADERSHIP AND COMMUNITY SERVICE

\vspace{-0.4cm}
\rule{\textwidth}{1pt}

**Course Assistant**, *Stanford Graduate School of Business* \hfill 2025   
Course assistant under Professor Katherine Casey. 

- a. Assisted on teaching activities for the Strategy Beyond Markets course at the Stanford Graduate School of Business. 
- b. Supported early- and mid-career MBA students on course content and concepts.
- c. Supported course organization and management. 

**Conference Co-Organizer,** *DevPec* \hfill April 2024    

- a. Co-organized the 2024 edition of the student-led Development and Political Economics Conference (DevPEC). 
- b. Collaborated with a team of PhD students from Stanford University's Economics Department and the University of Berkeley's Economics Department.

# AWARDS AND RESEARCH GRANTS

\vspace{-0.4cm}
\rule{\textwidth}{1pt}

**International Growth Centre Full Research Grant**, *&pound;75,000*   \hfill 2024      
**Local Government Revenue Initiative Grant**, *&euro;188,664*   \hfill 2024      
**Local Government Revenue Initiative Grant**, *USD &dollar;51,165*   \hfill 2024      
**International Growth Centre Small Projects Fund**, *&pound;19,000*   \hfill 2024      

# SKILLS AND INTERESTS

\vspace{-0.4cm}
\rule{\textwidth}{1pt}

**Languages:** English (Bilingual), Spanish (Native), French (Advanced), Portuguese (Advanced), Sierra Leonean Krio (Beginner).

**Programming and Statistical Packages:** R, Python, Stata, SPSS, SQL.

**Citizenship:** Dominican Republic.

# REFERENCES

\vspace{-0.4cm}
\rule{\textwidth}{1pt}

**Professor Katherine Casey**  
Stanford Graduate School of Business  
Academic supervisor within doctorate program  
*Email:* kecasey@stanford.edu

**Professor Caroline Hoxby**  
Stanford University Department of Economics  
Academic supervisor within doctorate program    
*Email:* choxby@stanford.edu  

**Professor Beatriz Magaloni-Kerpel**      
Stanford University Department of Political Science  
Academic supervisor within doctorate program  
*Email:* magaloni@stanford.edu

**Professor Wilson Prichard**       
Munk School of Global Affairs & Public Policy  
Co-author and policy collaborator  
*Email:* wilson.prichard@utoronto.ca


```{r eval=FALSE, include=FALSE}
**Statistical packages and programming languages:** 

**Survey Implementation:** SurveyCTO.

**Communication and collaboration:** LaTex, Git.
```

```{r eval=FALSE, include=FALSE}
# To render this file with Quarto, you can run:
#   quarto render support_material/cv_policy_multilaterals.qmd --to pdf
```
